Mining Interaction Log Data in a Creative Arts Practice using Transition Matrices

### 2015-09-24 flux-entropy-paper/flux-entropy-paper.tex
cleanups and nailing todos for results section

%\title{Quantitative Evaluation of Touch-Screen Group Musical Performance with
 % Transition Matrix Measures}
%\title{Mining interaction log data in long-term practice-led research}

@@

%in a Creative Arts Practice}

\numberofauthors{3}
\author{%
  \alignauthor{1st Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
  \alignauthor{2nd Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
  \alignauthor{3rd Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
     \alignauthor{4th Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
}

@@

In our corpus of iPad musical performances, logs of low-level touch-data record each performer's micro-gestures. 
Because it has been
established that musical performances on touch-screens can be chuncked into
vocabularies of continuous macro gestures that unfold over
several seconds of touch interaction~\cite{Martin:2014cr}, these logs
 can be thought of as a sequence of such
states~\cite{Pressing:1988uo} for each performer.
If a performers' touch interactions can be classified as belonging
to one of $m$ distinct states, then, over the course of a session, each
participant $X$ generates a length $N$ sequence of these interaction
states $X_n$ ($n = 1, \ldots, N$) which can be thought of as Markov
process.
If there is an (automated) classification process for identifying each
participant's state sequence from their interaction data, then we can
estimate the $m \times m$ transition matrix (TM), $P$, which characterises
this process by setting each entry, $p_{ij}$, to be the number of times
state $j$ follows state $i$ in the sequence. The transition activity
of the whole ensemble can be calculated by averaging the TM for each
performer. The matrix can be normalised so that the sum of all
elements is equal to one.

@@

For entropy, significant main effects were found due to session
context ($F(2,86) = 12.10, p < 0.001$), and instrumentation
($F(1,86) = 25.86$) (WHAT IS THE P VALUE HERE?). There was no main effect for session type although
 the interaction of session type and
instrumentation was found to be significant
($F(1,86) = 9.93, p<0.01$).

@@

@@

\subsection{Breaking Sessions into sections}

>>>>

%\title{Mining interaction log data in long-term practice-led research}

@@

\numberofauthors{3}
\author{%
  \alignauthor{1st Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
  \alignauthor{3rd Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
     \alignauthor{4th Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
}

@@

In our corpus of iPad musical performances, logs of low-level touch-data record each performer's micro-gestures. 
Because it has been
established that musical performances on touch-screens can contain 
vocabularies of continuous macro gestures that unfold over
several seconds of touch interaction~\cite{Martin:2014cr}, and that
gestural performances can be divided into sequences of such states~\cite{Pressing:1988uo}, these logs
 can be used identify a sequence of such states for each performer.
If a performers' touch interactions can be classified as belonging
to one of $m$ distinct states, then, over the course of a session, each
participant $X$ generates a length $N$ sequence of these interaction
states $X_n$ ($n = 1, \ldots, N$) which can be thought of as Markov
process.
If there is an (automated) classification process for identifying each
participant's state sequence from their interaction data, then we can
estimate the $m \times m$ transition matrix (TM), $P$, which characterises
this process by setting each entry, $p_{ij}$, to be the number of times
state $j$ follows state $i$ in the sequence. The transition activity
of the whole ensemble can be calculated by averaging the TM for each
performer. The matrix can be normalised so that the sum of all
elements is equal to one.

@@

For entropy, significant main effects were found due to session
context ($F(2,86) = 12.10, p < 0.001$), and instrumentation
($F(1,86) = 25.86, p < 0.001$).
There was no main effect for session type although
 the interaction of session type and
instrumentation was found to be significant
($F(1,86) = 9.93, p<0.01$).

@@

% R> summary(aov(flux~performance_context*performance_type*instruments, perf.sessions))
%                                                  Df Sum Sq Mean Sq F value
% performance_context                               2 0.0267  0.0133    6.28
% performance_type                                  1 0.0153  0.0153    7.21
% instruments                                       1 0.0426  0.0426   20.06
% performance_context:performance_type              1 0.0131  0.0131    6.18
% performance_context:instruments                   1 0.0000  0.0000    0.02
% performance_type:instruments                      1 0.0223  0.0223   10.48
% performance_context:performance_type:instruments  1 0.0034  0.0034    1.62
% Residuals                                        86 0.1828  0.0021        
%                                                   Pr(>F)
% performance_context                               0.0028
% performance_type                                  0.0087
% instruments                                      2.3e-05
% performance_context:performance_type              0.0149
% performance_context:instruments                   0.8954
% performance_type:instruments                      0.0017
% performance_context:performance_type:instruments  0.2065
% Residuals                                               
% R> summary(aov(entropy~performance_context*performance_type*instruments, perf.sessions))
%                                                  Df Sum Sq Mean Sq F value
% performance_context                               2   5.10    2.55   12.10
% performance_type                                  1   0.31    0.31    1.48
% instruments                                       1   5.46    5.46   25.87
% performance_context:performance_type              1   0.21    0.21    0.99
% performance_context:instruments                   1   0.10    0.10    0.49
% performance_type:instruments                      1   2.09    2.09    9.93
% performance_context:performance_type:instruments  1   0.01    0.01    0.04
% Residuals                                        86  18.14    0.21        
%                                                   Pr(>F)
% performance_context                              2.3e-05
% performance_type                                  0.2267
% instruments                                      2.1e-06
% performance_context:performance_type              0.3224
% performance_context:instruments                   0.4878
% performance_type:instruments                      0.0022
% performance_context:performance_type:instruments  0.8396
% Residuals                                               
% R>

@@

\subsection{Breaking sessions into sections}
